ASV visualization

### 2019-10-31 code/scratch/asv_viz.Rmd
moved this to scratch

```{r libs, echo=F}
library(tidyverse)
library(here)
library(DECIPHER)
library(ggforce)
library(Rtsne)
library(ape)
library(ggtree)
library(treeio)
library(dbscan)
library(ggthemes)
library(ggpubr)
# library(plotly)
# library(crosstalk)
# library(DT)
```

```{r set}
theme_set(theme_few())
set.seed(123)
```

@@

# extract the legend
tsne_plot %>% 
  get_legend() %>% 
  as_ggplot()
ggsave(here("figs","asv-cluster","asv-legend.pdf"), height = 7, width = 3)

# plot and save the main plot
tsne_plot +
  theme(legend.position = "none")
ggsave(here("figs","asv-cluster","asv-cluster.pdf"), height = 5, width = 5)
```

>>>>

```{r libs, echo=F}
library(tidyverse)
library(here)
library(DECIPHER)
library(ggforce)
library(Rtsne)
library(ape)
library(ggtree)
library(treeio)
library(dbscan)
library(ggthemes)
library(ggpubr)
library(ggdark)
# library(plotly)
# library(crosstalk)
# library(DT)
```

```{r set}
theme_set(theme_few())
```

@@

# extract the legend
tsne_plot %>% 
  get_legend() %>% 
  as_ggplot 
ggsave(here("figs","asv-cluster","asv-legend-dark.pdf"), height = 7, width = 3)

# plot and save the main plot
tsne_plot +
  theme(legend.position = "none")
ggsave(here("figs","asv-cluster","asv-cluster-dark.pdf"), height = 5, width = 5)
```
